A significance test in forward stepwise regression

### 2014-04-21 paper/paper.tex
Changed GAMSel to not be hierarchical

The covariance test (assuming $X$'s columns are of length one and $\Sigma = \sigma^2 I$ is at the
first step by
\begin{equation}
\label{eq:covtest}
T_1 = \frac{\lambda_1(\lambda_1-\lambda_2)}{\sigma^2} \overset{n,p \to \infty}{\to} \text{Exp}(1).
\end{equation}
In \cite{tests:adaptive} it is pointed out 
\begin{equation}
\label{test:exact}
\exp\left(- \frac{\lambda_1(\lambda_1-\lambda_2)}{\sigma^2} \right) \approx \frac{1 - \Phi(\lambda_1/\sigma)}{1 - \Phi(\lambda_2 / \sigma)} \overset{D}{=} \text{Unif}(0,1).
\end{equation}
Further, the above test statistic can be understood as the survival function of $\lambda_1 = \|X^Ty\|_{\infty}$
{\em conditional} on which variable achieves $\lambda_1$ as well as its sign.
The limiting results about later steps in \cite{significance:lasso} can (formally) be interpreted as
recursively applying $T_1$ to the variables that had not previously been selected by LARS.

@@

The \emph{group lasso estimator} is a solution to the following convex
problem
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation}
\begin{aligned}
\label{eq:gsoln}
\displaystyle \hat \beta_\lambda = \argmin_{\beta \in \real^p} \frac{1}{2} \| y - X \beta \|_2^2 +
   \lambda \sum_{g=1}^G w_g \| \beta_g \|_2
\end{aligned}
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The parameter $\lambda \geq 0$ enforces sparsity in groups: for large
$\lambda$ most of the $\beta_g$ will be zero vectors. The weights
$w_g$ are usually taken to be $\sqrt {p_g}$ to normalize the penalty
across groups.  Note that this includes the usual lasso estimator as a
special case when all of the groups are of size 1, since then the
penalty term is the $L^1$-norm of $\beta$.

There is a largest value of $\lambda$ such that $\hat{\beta}_{\lambda}=0$ which corresponds to $\lambda_1$
in the LASSO setting:
\begin{equation}
\label{eq:lammax}
\lambda_1^{\text{group}} = \max_{g} \frac{1}{w_g}\|X_g^Ty\|_2 . 
\end{equation}
Formally, the value above is just the dual norm of the penalty
$$
{\cal P}(\beta) = \sum_{g=1}^G w_g \| \beta_g \|_2
$$
hence it can be expressed as
\begin{equation}
\label{eq:lammax}
\lambda_1^{\text{group}} = \max_{g} \frac{1}{w_g}\|X_g^Ty\|_2 = \frac{1}{w_{g^*}}\eta_{g^*}^TX_{g^*}^Ty . 
\end{equation}
where $g^*$ is the group that achieves the max and 
$\eta_{g^*} = X_{g^*}^Ty / \|X_{g^*}^Ty\|_2$ is the $\ell_2$ unit vector that achieves $\|X_{g^*}^Ty\|_2$.

>>>>

The covariance test (assuming groups of size one and $\Sigma = \sigma^2 I$ is given at the first step by
\begin{equation}
\label{eq:covtest}
T_1 = \frac{\lambda_1(\lambda_1-\lambda_2)}{\sigma^2} \overset{n,p \to \infty}{\to} \text{Exp}(1).
\end{equation}
In \cite{tests:adaptive} it is pointed out 
\begin{equation}
\label{test:exact}
\exp\left(- \frac{\lambda_1(\lambda_1-\lambda_2)}{\sigma^2} \right) \approx \frac{1 - \Phi(\lambda_1/\sigma)}{1 - \Phi(\lambda_2 / \sigma)} \overset{D}{=} \text{Unif}(0,1).
\end{equation}
Further, the above test statistic can be understood as the survival function of $\lambda_1 = \|X^Ty\|_{\infty}$
{\em conditional} on which variable achieves $\lambda_1$ as well as its sign.
The limiting results about later steps in \cite{significance:lasso} can (formally) be interpreted as
recursively applying $T_1$ to the variables that had not previously been selected by LARS.

@@

The \emph{group lasso estimator} is a solution to the following penalized
least-squares convex optimization problem
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation}
\begin{aligned}
\label{eq:gsoln}
\displaystyle \hat \beta_\lambda = \argmin_{\beta \in \real^p} \frac{1}{2} \| y - X \beta \|_2^2 +
   \lambda {\cal P}(\beta) \\
\end{aligned}
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
with the group penalty
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation}
  \begin{aligned}
  \label{eq:gpen}
    {\cal P}(\beta)&= \sum_{g=1}^G w_g \| \beta_g \|_2 \\
  \end{aligned}
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The parameter $\lambda \geq 0$ enforces sparsity in groups: for large
$\lambda$ most of the $\beta_g$ will be zero vectors. The weights
$w_g$ are usually taken to be $\sqrt {p_g}$ to normalize the penalty
across groups with different sizes.  Note that this includes the usual lasso estimator as a
special case when all of the groups are of size 1, since then the
penalty term is the $L^1$-norm of $\beta$. The solution path of the group
lasso has similar properties to the lasso case, however it is not
generally piecewise linear.

For sufficiently large $\lambda$ the solution to~\eqref{eq:gsoln} is forced
to be zero. The smallest such $\lambda$ is denoted
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation}
  \begin{aligned}
   \lambda_1 &= \inf \{ \lambda \geq 0 : \hat \beta_{\lambda'} = 0 \text{ for all } \lambda' > \lambda \} \\
  \end{aligned}
\end{equation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the LASSO setting this is explicitly computable by
\begin{equation}
\label{eq:lammax}
\lambda_1^{\text{group}} = \max_{g} \frac{1}{w_g}\|X_g^Ty\|_2 . 
\end{equation}
The value above is also the dual norm of the penalty~\eqref{eq:gpen}
hence it can be expressed as
\begin{equation}
\label{eq:lammax}
\lambda_1^{\text{group}}
% = \max_{g} \frac{1}{w_g}\|X_g^Ty\|_2
 = \frac{1}{w_{g^*}}\eta_{g^*}^TX_{g^*}^Ty . 
\end{equation}
where $g^*$ is the group that achieves the max and 
$\eta_{g^*} = X_{g^*}^Ty / \|X_{g^*}^Ty\|_2$ is the unit vector that achieves $\|X_{g^*}^Ty\|_2$.
